Toward theories of deliberated preferences

### 2020-11-16 simple.tex
Typo symbol

To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\leadsto$. Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
The following example may help forging an intuition about what the possible falsifying sets of observations are.
\begin{example}[Falsification sequences]
	Let us examine the possible observations that would suffice to show that the theory presented in our running example is not Convincing.

>>>>

To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\allleadsto$. Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
The following example may help forging an intuition about what the possible falsifying sets of observations are.
\begin{example}[Falsification sequences]
	Let us examine the possible observations that would suffice to show that the theory presented in our running example is not Convincing.
